### 2019-02-23 manuscript/results.tex
filled in the table of median rate estimates

\section{Results}
\subsection{Polyploidy and Diversification Models}
Similarly to the results obtained by \citet{mayrose_2011} and \citet{mayrose_2015}, we found that in the D/P polyploidy model the net diversification of diploids is larger than the the net diversification of polyploids since the net diversification distributions do not overlap (Figure 2(A)). This result holds true whether or not the diploidization parameter is present. However in the presence of  the diploidization parameter the net diversification rate of polyploids is nonnegative with probability 1 (Figure 2(A)), whereas in the absence of diploidization the net diversification rate of polyploids can be negative with a probability (HERE verify the quantile) (FIGURE 3(A)). In terms of the relative extinction, when the diploidization parameter is present both polyploids and diploids have posterior distributions that overlap, but that pattern changes in the absence of the diploidization parameter leading to a significant difference between relative extinction where polyploids have a significant higher relative extinction rate (see Supplementary Information).\newline

@@

% E & B:  We just spent awhile poring over the great supp figures of rate estimates, which are essential to grasp the uncertainties.  But to facilitate quick comparisons across models, could we have a table of the median rate estimates for all models?  Possibly like the format I've laid out below?  Or maybe there's a better way.

\begin{supptable}
    \begin{center}
    \begin{tabular}{lcccccc}
                       & D/P & D/P+A/B & I/C & I/C+A/B & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %
        $r_D$          &     &         & --- & ---     & ---      & ---          \\
        $r_P$          &     &         & --- & ---     & ---      & ---          \\
        $r_I$          & --- & ---     &     &         & ---      & ---          \\
        $r_C$          & --- & ---     &     &         & ---      & ---          \\
        $r_{ID}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CD}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CP}$       & --- & ---     & --- & ---     &          &              \\
        %
        $\rho$         &     &         & --- & ---     & ---      & ---          \\
        $\rho_I$       & --- & ---     & --- & ---     &          &              \\
        $\rho_C$       & --- & ---     & --- & ---     &          &              \\
        $\delta$       &     &         &     &         &          &              \\
        $q_{IC}$       & --- & ---     &     &         &          &              
    \end{tabular}

    \vspace{12pt}
    \begin{tabular}{lcccccc}
                       & D/P & D/P+A/B & I/C & I/C+A/B & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %
        $r_D$          &     &         & --- & ---     & ---      & ---          \\
        $r_P$          &     &         & --- & ---     & ---      & ---          \\
        $r_I$          & --- & ---     &     &         & ---      & ---          \\
        $r_C$          & --- & ---     &     &         & ---      & ---          \\
        $r_{ID}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CD}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CP}$       & --- & ---     & --- & ---     &          &              \\
        %
        $\rho$         &     &         & --- & ---     & ---      & ---          \\
        $\rho_I$       & --- & ---     & --- & ---     &          &              \\
        $\rho_C$       & --- & ---     & --- & ---     &          &              \\
        $q_{IC}$       & --- & ---     &     &         &          &              
    \end{tabular}
    \end{center}
    \caption{median rate estimates for all models (see supp figs for more details and uncertainties); when there are two numbers in one cell, they're for the A and B hidden states; --- means that parameter was not present in the model; upper section is for models with $\delta$ and lower section is for models without}
    \label{table:estimates}
\end{supptable}

>>>>

\section{Results}

%B: IMO each instance of "(Figure 2(X))" ought be replaced with "(Figure 2x)", so that (Figure 2(A)) becomes (Figure 2a). Double-parentheses should be reserved for equations and we already use caps, for example C and D, for traits. I am happy to make the change in the text, which is trivial, but I am not sure how the PDF conversion through illustrator would fare.

\subsection{Polyploidy and Diversification Models}
Similarly to the results obtained by \citet{mayrose_2011} and \citet{mayrose_2015}, we found that in the D/P polyploidy model the net diversification of diploids is larger than the the net diversification of polyploids since the net diversification distributions do not overlap (Figure 2(A)). This result holds true whether or not the diploidization parameter is present. However in the presence of  the diploidization parameter the net diversification rate of polyploids is nonnegative with probability 1 (Figure 2(A)), whereas in the absence of diploidization the net diversification rate of polyploids can be negative with a probability (HERE verify the quantile) (FIGURE 3(A)). In terms of the relative extinction, when the diploidization parameter is present both polyploids and diploids have posterior distributions that overlap, but that pattern changes in the absence of the diploidization parameter leading to a significant difference between relative extinction where polyploids have a significant higher relative extinction rate (see Supplementary Information).\newline

@@

\begin{supptable}
    \begin{center}
    \begin{tabular}{lcccccc}
                       & D/P   & D/P+A/B      & I/C    & I/C+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                                                      
        $r_D$          & 0.382 & 0.698, 0.100 & ---    & ---          & ---      & ---          \\
        $r_P$          & 0.109 & 0.587, 0.182 & ---    & ---          & ---      & ---          \\
        $r_I$          & ---   & ---          & 0.550  & 0.386, 0.877 & ---      & ---          \\
        $r_C$          & ---   & ---          &-0.001  &-0.059, 0.606 & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & ---    & ---          & 0.449    & 0.318, 0.789 \\
        $r_{CD}$       & ---   & ---          & ---    & ---          & 0.050    &-0.248, 0.494 \\
        $r_{CP}$       & ---   & ---          & ---    & ---          &-0.027    & 0.110, 0.634 \\
        %                                                                                      
        $\rho$         & 0.033 & 0.026        & ---    & ---          & ---      & ---          \\
        $\rho_I$       & ---   & ---          & ---    & ---          & 0.063    & 0.047        \\
        $\rho_C$       & ---   & ---          & ---    & ---          & 0.024    & 0.011        \\
        $\delta$       & 0.050 & 0.162        & ---    & ---          & 0.022    & 0.107        \\
        $q_{IC}$       & ---   & ---          & 0.364  &              & 0.194    & 0.164        
    \end{tabular}

    \vspace{12pt}
    \begin{tabular}{lcccc}
                       & D/P   & D/P+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                              
        $r_D$          & 0.260 & 0.193, 0.658 & ---      & ---          \\
        $r_P$          &-0.056 & 0.030, 0.187 & ---      & ---          \\
        $r_I$          & ---   & ---          & ---      & ---          \\
        $r_C$          & ---   & ---          & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & 0.455    & 0.309, 0.797 \\
        $r_{CD}$       & ---   & ---          & 0.065    &-0.006, 0.587 \\
        $r_{CP}$       & ---   & ---          &-0.088    &-0.074, 0.403 \\
        %                                                              
        $\rho$         & 0.047 & 0.047        & ---      & ---          \\
        $\rho_I$       & ---   & ---          & 0.067    & 0.053        \\
        $\rho_C$       & ---   & ---          & 0.033    & 0.032        \\
        $q_{IC}$       & ---   & ---          & 0.198    & 0.145        
    \end{tabular}
    \end{center}
    \caption{
        Median rate estimates for all models.
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
        The upper section is for models with diploidization, and the lower section is for models without.
        The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}
